Real-space computation of $E$/$B$-mode maps I: Formalism, Compact Kernels, and Polarized Filaments

### 2018-10-05 articles/jcap_referee_response/Response to referee/response to referee.tex

\documentclass[12pt]{article}

\usepackage[latin1]{inputenc}
\usepackage{amsmath, amsfonts, amssymb, hyperref, graphicx, multirow, subfigure, bbold}
\hypersetup{colorlinks=True,citecolor=blue}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[normalem]{ulem}
\usepackage{caption}
\usepackage{array}

\newcommand{\st}{\sout}
\newcommand{\revisit}{\textcolor{magenta}}
\newcommand{\comment}{ $\Rightarrow$ \textcolor{blue}  }
\newcommand{\rfedit}{\textcolor{magenta}}
\newcommand{\addtext}{\textcolor{BlueViolet}  }

\begin{document}

\title{Response to referee}
\author{Aditya Rotti and Kevin Huffenberger}
\date{}
\maketitle

We would like to thank the referee for a careful reviewing of our paper.  Below we systematically respond to each of the points raised by the referee, within the scope of the work presented in this article. Where necessary, we have made appropriate edits to the draft which are highlighted in \textcolor{magenta}{magenta} colored text.

\begin{itemize}

\item[{Referee comment: }] The real space formalism looks very helpful, but it is unclear what a mask can do to the E/B mixing. The E/B leakage due to masking is inevitable as Ref. [31] argued, but it is not discussed. Also, some brief comparison with the conventional approaches in the literature, such as the pure estimator (astro- ph/0511629), could be added to explain why such a real space approach is necessarily required and why it is more advantageous.
\item[{Authors response: }] We agree that masking induced $E/B$ mixing is an important issue pertinent to this translation from the spinorial to scalar description of the polarization field, however this is beyond the scope of this paper. As noted in the paper, this is a first in a series of papers and the next paper(in preparation) will discuss and detail the implementation of these real space operators, their comparison to conventional methods and issues related to masking. We do not argue that real space method is necessarily advantageous, instead we present the formalism as an alternate methodology for carrying out analysis of spin fields on the sphere. %This complementary analysis route, alternative analysis strategies which may not be possible using conventional approaches. 
\comment{Add a line to the draft.}

\item[{Referee comment: }]  At the end of paragraph 5 in the introduction, it says ?... for minimizing foreground contamination...?. Similar to the question above, it looks like the main motivation is the foreground isolation but it is not discussed.
Maybe this is still related to the first question. 
\item[{Referee comment: }] We do allude to the speculative idea of alternative methods of dealing with mitigation problems of foreground mitigation using tunable real space kernels as one of the motivations, however we are at this moment unable to discuss this in further detais.\\

\item[{Referee comment: }] The authors derived the radiation and convolution kernels that are shown in Figs. 3 and 4. It is still unclear to me what the E/B power spectra look like from this real-space computation. For example, the authors can make a quick simulation on a small patch or the full-sky to easily validate that the E/B power spectra are correctly recovered from this real space computation.

\item[{Referee comment: }]  Our main aim in this paper was to layout the formalism for real space evaluations of $E/B$ fields from the measured Stokes $Q/U$ parameters and highlight and discuss in detail the two different interpretations, namely the ``radiation" and ``convolution" forms of the real space kernels. Please see the supplementary section at the end of this response, where we present some results from real space evaluation of E/B maps and the corresponding power spectra.\\

\item[{Referee comment:}] What is the time complexity of the real space transformation? Eq. (3.26) seems to indicate it is actually $O(N_{\rm pix}^2 )$ which is not as efficient as the conventional approaches. If possible, the authors could briefly discuss it.

\item[{Authors response:}] Yes, naively the real space implementation which is perfectly equivalent to conventional methods would scale as $O(N_{\rm pix}^2 )$. However we have noted that this scaling could be significantly improved by reconstructing some filtered versions $E/B$ fields, which will have a better scaling. We are in process of quantifying this relative efficiency and plan to report our finding in a subsequent publication. \comment{Comment on computation time and clarify on computation time.}

\item[{Referee comment: }]It looks like the real part (E) and imaginary part (B) can be easily calculated from Eq. (3.8). It is unclear why the purifying procedure ? Eq. (3.25) is needed. The authors should explain it at the beginning of section 3.4. Also, the maps $\bar P_E$ and $\bar P_B$ in Eqs. (3.17) and (3.18) should be explicitly written down using E and B modes like Eq. (2.8).

\item[{Authors respone: }] As stated in the text at the beginning of Sec.~(3.4), the main point is that we present an operator which directly decomposes the total Stokes vector into a component that purely contributes to E-modes and another which contributes  to B-modes, \emph{without first having to evaluate the $E/B$ modes themselves.} One can ofcourse carry out this operation by first evaluating the $E$ \& $B$ mode maps and then translating these individually to the corresponding Stokes vector. This procedure can be evaluated by following the procedure outlined in Sec. (3.1) and Sec.(3.2). %Note that this alternate procedure would be twice as expensive, as compared to the procedure outlined in Sec.(3.4). 
\comment{It is interesting to look at the kernels.}

\item[{Referee comment: }] In the first row of Fig. 3, why is the color/pattern of the third plot so different from the rest? Is there any numerical issue with the pole? Why is necessary to show the location of the North Pole in Fig. 3?

\item[{Authors response: }] The plot has been revised to match the color scale in other plots in Fig. 3.

Note that the third plot in first row of Fig. 3, depicts the $Q$ pattern correspond to $E$ field which is non-vanishing only at the north pole (or $U$ pattern due to $B$ field which is non-zero only at the north pole). For this special setting the $Q$(or $U$) are expected to have angular symmetry while their amplitude is modulated in the radial direction by ${}_{\mathcal{M}}f$. Kindly note Eq. 3.15 and 3.16 which encode these details.

\item[{Referee comment: }] Section 3.5 fails to explain what the non-locality is, why it matters, especially how that is connected to the E/B separation problem. Also, what is the implication of the band limit dependence for E/B separation problem? Is there any first-principle calculation of the value $\ell_0$ that is purely phenomenological in the text?

\item[{Authors response: }] \addtext{We have made appropriate revisions in text to highlight the relevance of this section.} A high band limit causes the radial function to be more sharply peaked in the vicinity of the location of where the $E/B$ fields are being evaluated, as depicted in Fig.6. It is this property of the radial kernels that  clarifies why techniques of mask apodization help mitigate the $E/B$ mixing problem.%, as it explains why the leakage field is large in the vicinity of where the mask transitions from 1 to 0. $\ell_0$ is derived purely empirically as it only suggests an indicative non-locality parameter $\beta_0$.

\item[{Referee comment: }] Given the oscillatory feature in Fig. 6, is there any technical difficulty for getting a good convergence for the real space transformation when the radiation/convolution kernels are sampled at discrete pixels? Is there any convergence criterion?
\item[{Authors response: }]  The oscillatory nature of the radial kernels shown in Fig. 3 emanates purely from sums over associated Legendre polynomials, where the limits of summation are set by the band limit. There is no convergence issue related to evaluating these kernels. The discretized pixels only result in sampling these radial kernels at specific arguments.

\item[{Referee comment: }] For any subplot shown in Fig.~6, is the pixel size $\Delta \Omega$ a fixed value or varying at different lmax? Can the authors clarify this? It seems to indicate that the resulting E/B power spectra will depend on the lmax even for the same Q/U maps. Or simply, how would the lmax be chosen for a given experiment if the transformation kernel is dependent of lmax?
\item[{Authors response: }] Generation of Fig.~6 does not depend on pixel size $\Delta \Omega$. The figures (\rm i,\rm {ii},\rm {iii}) in the top panel of Fig. 6 are generated by evaluating the respective summations over associated Legendre polynomials on an arbitrarily finely spaced grid of angular separation $\beta$. These specific figures depict the radial kernels that would go into evaluating the real space kernels on the sphere.\\
$~~~~$The plot in the bottom of Fig.~6 (\rm iv, \rm v) result from evaluating a moving average with window of size $0.3 \beta_0$ on the respective radial kernels and these are presented to demonstrate that the average behaviour of the oscillatory radial kernels matches the scaling behaviour argued in Zaldariagga (2001).

\item[{Referee comment: }] With a high value of $\ell_{\rm max}$, it looks like only the neighboring pixels are important for the kernels. What is the ratio of $\beta_0/\sqrt{\Delta \Omega}$ at different $\ell_{max}$? As Fig.~7 indicates, is the portion $\theta > 3\beta_0$ just neglected to speed up the computation? If true, how big is the error?
\item[{Authors response: }] In this work we do not compute the $E/B$ maps to evaluate and asses the quality of the corresponding spectra. The purpose of Fig.~7 is to present some example radial kernels, their respective harmonic space representations and the resultant harmonic space filters which would be needed to evaluate the default $E/B$ mode spectra. Implementation details of the real space operators and assessing the quality of the reconstructed $E/B$ maps and the corresponding spectra is the subject of follow up work on this topic. For a simple demonstration see the supplementary section.

%\revisit{The ratio $\beta_0/\sqrt{\Delta \Omega} = \frac{\pi \ell_0/\ell_{\rm max}} \frac{\sqrt{4 \pi}}{\sqrt{12 N_{\rm side}^2-1}}$

\item[{Referee comment: }] In Fig. 7, the authors need to discuss a few aspects for the chosen example of the modified radial function, including what motivates this form, how this is done for the real-space maps and how it is reconstructed. A fractional error is seen from the input (red) and reconstructed (dashed black) so there might be a leakage from the E modes into B modes. Ideally the reconstruction at any $\ell_{\rm max}$ should work, for example $\ell_{\rm max} = 768$, not just limited to 1536. Can the authors verify this?
\item[{Authors response: }] The red curve is motivated by demanding that the radial kernel have a compact support, unlike the default radial kernel ${}_\mathcal{M} f$ which spans the complete domain $\theta \in [0,\pi]$. In Fig.~7, the black curve represents the band limited ($\ell_{\rm max}=1536$) reconstruction of the red curve and the error represents the inability to reconstruct the red curve given the band limit. This is likely to limit the reconstruction of large scale $E/B$ modes, however it will not result in $E/B$ mixing. The details of how this would be implemented on real data and assessing the quality of $E/B$ reconstruction are beyond the scope of this work. However, for a simple demonstration see the supplementary section.

\item[{Referee comment: }] It is unclear what motivates the discussion of section 4 on page 19. The authors should add some introductory text at the beginning of section 4 to connect it to the previous sections.
\item[{Authors response: }] \addtext{We have appropriate text at the beginning of Sec. 4.}

\item[{Referee comment: }] A few definitions are missing: $\bar P_E$ and $\bar P_B$ in Eqs.~(3.17) and (3.18), ${}_{+2} X_{E/B}$ in Eq. (3.26), ${}_\mathcal{M} f$ in Eq. (3.5c), $N_{\rm pix}$ and $N_{\rm alm}$ in Eq. (2.9).
\item[{Authors response: }] Eqs.~(3.17),  Eq.~(3.18) and Eq. (3.26) serve as definitions of the variables $\bar P_E$, $\bar P_B$ and ${}_{+2} X_{E/B}$ respectively. Going from Eq.~(3.5b) to Eq.~(3.5c) defines ${}_\mathcal{M} f$ by association. The text has now been appropriately modified to explicitly define $N_{\rm pix}$ and $N_{\rm alm}$.

\item[{Referee comment: }] Fig. 5 seems to be redundant because Fig. 6 shows the same content although in log scale. The authors should mention the difference between the two.
\item[{Authors response: }] Yes Fig.~(5) and Fig.~(6) decpict the same radial kernels, however Fig.~(5) serves to clearly show some of the features of the radial kernel which are not visible in the log-scale version of the plot. For instance the negatives of the radial kernel, the vanishing of ${}_\mathcal{M}f$ etc...

\item[{Referee comment: }] Figs 6 and 7 are not legible.
\item[{Authors response: }] \addtext{The label sizes have been revised to make the figures more legible.}

\end{itemize}

\section*{Supplementary}
We note that, many of the questions raised by the referee, are relevant, but beyond the scope of the work presented in this article. Most of these questions form the topic of our follow up work, where we discuss the implementation details of the real space operator, their comparison to conventional approaches, E/B mixing on masked skies using these real space kernels, etc.

Since the referee has asked many question pertaining to issues relating to actual implementations, here we present some results from our follow up work.

\end{document}

### 2018-10-05 articles/jcap_referee_response/modified article jcap/article.tex
renamed folder to a more appropriate name

% Text comments and highlights
\newcommand{\st}{\sout}
\newcommand{\revisit}{\textcolor{red}}
\newcommand{\comment}{ $\Rightarrow$ \textcolor{green}  }
\newcommand{\rfedit}{\textcolor{magenta}  }
\newcommand{\soothe}{\textcolor{BlueViolet}  }

@@

\subsection{Matrix notation} \label{sec:mat_pol_intro}
Our derivations of the real space operators are more transparent in a matrix-vector notation\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}. We introduce a matrix that encodes spin spherical harmonic basis vectors:
%
\beq
{}_{|s|}\mathcal{Y}= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} ;\qquad  {}_{|s|}\mathcal{Y}^{\ddagger}= \Delta \Omega \bmat _{+s}Y^{\dagger} & 0 \\ 0 & _{-s}Y^{\dagger} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm pix}} \,,
\eeq
%
where $s$ denotes the spin of the basis functions and our definition of ${}_{|s|}\mathcal{Y}^{\ddagger}$ differs from the conventional conjugate transpose operation by the factor $\Delta \Omega$.  We introduce this to ensure the orthonormality of these operations on the discretized sphere when the pixel size is sufficiently small, ${}_{|s|}\mathcal{Y}^{\ddagger} {}_{|s|}\mathcal{Y} = I_{2 \rm N_{\rm alms} \times2 \rm N_{\rm alms}}$, and also maintain the standard definition of spherical harmonics.

@@

The kernels $\mathcal{D}$ and $\mathcal{I}$ vary significantly as a function of galactic latitude of the central pixel, as seen in \fig{fig:vis_kernel_DI}. These kernels show a two fold symmetry in the vicinity of the poles, which can be understood as a consequence of the Euler angle $\gamma \approx 0$ here and therefore $e^{i2(\alpha \pm \gamma)} \approx e^{i2\alpha}$. Note that in this region, the azimuthal profile of the real and imaginary part of these kernels is identical to $-\mathcal{M}^*_G$.  The imaginary part of the band limited delta function $\mathcal{I}$ contributes just as much as the real part in these regions. On transiting to lower latitudes, however, $\mathcal{D}$ quickly transitions to having a four fold symmetry while $\mathcal{I}$ transitions to being dominated by the real part and behaves more like the conventional delta function. This transition can be most easily understood in the flat sky limit where $\gamma \approx -\alpha$ which leads to the resultant 4 fold symmetry seen for $\mathcal{D}$ owing to $e^{i2(\alpha - \gamma)} \approx e^{i4\alpha}$ and $\mathcal{I}$ being dominated by the real part owing to $e^{-i2(\alpha + \gamma)} \approx 1 + i0$. Since the flat sky approximation has most validity in the proximity of the equator these limiting tendencies of the respective kernels are seen in the bottom row of \fig{fig:vis_kernel_DI} which depict the kernels evaluated at the equator $b=0^{\circ}$. The middle two row depict the kernels evaluated at intermediate latitudes: $b=87^{\circ}$ and $b=80^{\circ}$ and serve to indicate the rate of this transition. As before, these kernels are invariant under changes in longitude of the central pixel with the latitude fixed.
%---------------------------------------------------------------------------------------------------------
%\include{kernel_discussion}
\subsection{The non-locality of the real space operators} \label{sec:radial_locality}
%
\begin{figure}[t]
\centering
\includegraphics[width=0.8\columnwidth]{beta_kernel.pdf}
\caption{The figure depicts the radial part of the convolution kernels. These radial function have been evaluated with the band limit fixed at $\ell \in [2,24]$. The vertical dashed line marks the approximate Healpix pixel size of a $N_{\rm side}=8$, which is the lowest resolution that allows access to $\ell_{\rm max}=24$.}
\label{fig:beta_kernel}
\end{figure}
%
Above, we have explored in detail the  azimuthal dependence of the real space kernels.  Here we probe the radial dependence, which both  determines the non-locality of the operators and encodes all their multipole dependencies. For illustration, \fig{fig:beta_kernel} shows the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$, evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,24]$. We choose such a low band limit to highlight some key features of their radial profile.
%
\begin{figure}[t]
\subfigure[\label{fig:fbeta}]{\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax.pdf}}\hfill
\subfigure[\label{fig:dfbeta}]{\includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}}\hfill
\subfigure[\label{fig:ifbeta}]{\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}}\hfill
\centering
\subfigure[\label{fig:fbeta_avg}]{\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax_zaldariagga_scaling.pdf}}
\subfigure[\label{fig:dfbeta_avg}]{\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax_zaldariagga_scaling.pdf}}

\caption{This figures depicts the radial functions for the different kernels and varying band limit, set by fixed $\ell_{\rm min}=2$ and varied $\ell_{\rm max}$ as indicated. \fig{fig:fbeta} depicts ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ the kernel for $Q/U$ to $E/B$ and vice versa. \fig{fig:dfbeta} depicts ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ and  \fig{fig:ifbeta} depicts ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, the Stokes purification kernels. All the curves are normalized such that their maxima is set to unity. The horizontal solid black line marks the location where the amplitude of the respective kernels fall below 1\% of its maximum. The thin slanted dashed gray lines indicate a power law fit (by eye) to the envelope of the radial functions. The thick black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0={\rm min}(180^\circ,180^\circ \times 22/\ell_{\rm max})$.  We show moving averages over oscillations in \fig{fig:fbeta_avg} and  \fig{fig:dfbeta_avg}.  They depict the radial functions $\langle{_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ and $\langle{_{\md}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ respectively where $\langle \cdots \rangle$ denotes a moving average over a step function centered at $\beta$ with a width $1.4\beta_0$. These smoothed functions are seen to be well fit by a power law $\propto \beta^{-2}$  and depict the average radial response.}
\label{fig:rad_ker_decay}
\end{figure}
%

>>>>

% Text comments and highlights
\newcommand{\st}{\sout}
\newcommand{\revisit}{\textcolor{red}}
\newcommand{\comment}{ $\Rightarrow$ \textcolor{green}  }
\newcommand{\rfedit}{\textcolor{magenta}  }
\newcommand{\addtext}{\textcolor{magenta}  }
\newcommand{\soothe}{\textcolor{BlueViolet}  }

@@

\subsection{Matrix notation} \label{sec:mat_pol_intro}
Our derivations of the real space operators are more transparent in a matrix-vector notation\footnote{While we work with the matrix and vector sizes given in terms of some pixelization parameter $\rm N_{\rm pix}$, all the relations are equally valid in the continuum limit attained by allowing $\rm N_{\rm pix}\rightarrow \infty$}. We introduce a matrix that encodes spin spherical harmonic basis vectors:
%
\beq
{}_{|s|}\mathcal{Y}= \bmat _{+s}Y & 0 \\ 0 & _{-s}Y \emat _{2 \rm N_{\rm pix} \times 2 \rm N_{\rm alms}} ;\qquad  {}_{|s|}\mathcal{Y}^{\ddagger}= \Delta \Omega \bmat _{+s}Y^{\dagger} & 0 \\ 0 & _{-s}Y^{\dagger} \emat _{2 \rm N_{\rm alms} \times 2 \rm N_{\rm pix}} \,,
\eeq
%
where $s$ denotes the spin of the basis functions, \addtext{$N_{pix}$ denotes the number of pixels on the sphere and $N_{alms}$ denotes the number of spherical harmonic coefficients of expansion.} %and
Note that our definition of ${}_{|s|}\mathcal{Y}^{\ddagger}$ differs from the conventional conjugate transpose operation by the factor $\Delta \Omega$.  We introduce this to ensure the orthonormality of these operations on the discretized sphere when the pixel size is sufficiently small, ${}_{|s|}\mathcal{Y}^{\ddagger} {}_{|s|}\mathcal{Y} = I_{2 \rm N_{\rm alms} \times2 \rm N_{\rm alms}}$, and also maintain the standard definition of spherical harmonics.

@@

The kernels $\mathcal{D}$ and $\mathcal{I}$ vary significantly as a function of galactic latitude of the central pixel, as seen in \fig{fig:vis_kernel_DI}. These kernels show a two fold symmetry in the vicinity of the poles, which can be understood as a consequence of the Euler angle $\gamma \approx 0$ here and therefore $e^{i2(\alpha \pm \gamma)} \approx e^{i2\alpha}$. Note that in this region, the azimuthal profile of the real and imaginary part of these kernels is identical to $-\mathcal{M}^*_G$.  The imaginary part of the band limited delta function $\mathcal{I}$ contributes just as much as the real part in these regions. On transiting to lower latitudes, however, $\mathcal{D}$ quickly transitions to having a four fold symmetry while $\mathcal{I}$ transitions to being dominated by the real part and behaves more like the conventional delta function. This transition can be most easily understood in the flat sky limit where $\gamma \approx -\alpha$ which leads to the resultant 4 fold symmetry seen for $\mathcal{D}$ owing to $e^{i2(\alpha - \gamma)} \approx e^{i4\alpha}$ and $\mathcal{I}$ being dominated by the real part owing to $e^{-i2(\alpha + \gamma)} \approx 1 + i0$. Since the flat sky approximation has most validity in the proximity of the equator these limiting tendencies of the respective kernels are seen in the bottom row of \fig{fig:vis_kernel_DI} which depict the kernels evaluated at the equator $b=0^{\circ}$. The middle two row depict the kernels evaluated at intermediate latitudes: $b=87^{\circ}$ and $b=80^{\circ}$ and serve to indicate the rate of this transition. As before, these kernels are invariant under changes in longitude of the central pixel with the latitude fixed.
%---------------------------------------------------------------------------------------------------------
%\include{kernel_discussion}
\subsection{The non-locality of the real space operators} \label{sec:radial_locality}
%
\begin{figure}[t]
\centering
\includegraphics[width=0.8\columnwidth]{beta_kernel.pdf}
\caption{The figure depicts the radial part of the convolution kernels. These radial function have been evaluated with the band limit fixed at $\ell \in [2,24]$. The vertical dashed line marks the approximate Healpix pixel size of a $N_{\rm side}=8$, which is the lowest resolution that allows access to $\ell_{\rm max}=24$.}
\label{fig:beta_kernel}
\end{figure}
%
Above, we have explored in detail the  azimuthal dependence of the real space kernels.  Here we probe the radial dependence, which both  determines the non-locality of the operators and encodes all their multipole dependencies. For illustration, \fig{fig:beta_kernel} shows the radial kernels ${_{\mm}f}, {_{\md}f},{_{\mi}f}$, evaluated using the respective multipole sums given in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} in the band limit $\ell \in [2,24]$. We choose such a low band limit to highlight some key features of their radial profile.
%
\begin{figure}[t]
\subfigure[\label{fig:fbeta}]{\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax.pdf}}\hfill
\subfigure[\label{fig:dfbeta}]{\includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax.pdf}}\hfill
\subfigure[\label{fig:ifbeta}]{\includegraphics[width=0.325\columnwidth]{rad_ker_i_fn_of_ellmax.pdf}}\hfill
\centering
\subfigure[\label{fig:fbeta_avg}]{\includegraphics[width=0.325\columnwidth]{rad_ker_fn_of_ellmax_zaldariagga_scaling.pdf}}
\subfigure[\label{fig:dfbeta_avg}]{\includegraphics[width=0.325\columnwidth]{rad_ker_d_fn_of_ellmax_zaldariagga_scaling.pdf}}

\caption{This figures depicts the radial functions for the different kernels and varying band limit, set by fixed $\ell_{\rm min}=2$ and varied $\ell_{\rm max}$ as indicated. \fig{fig:fbeta} depicts ${_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})$ the kernel for $Q/U$ to $E/B$ and vice versa. \fig{fig:dfbeta} depicts ${}_{\md}f(\beta,\ell_{\rm min},\ell_{\rm max})$ and  \fig{fig:ifbeta} depicts ${}_{\mi}f(\beta,\ell_{\rm min},\ell_{\rm max})$ respectively, the Stokes purification kernels. All the curves are normalized such that their maxima is set to unity. The horizontal solid black line marks the location where the amplitude of the respective kernels fall below 1\% of its maximum. The thin slanted dashed gray lines indicate a power law fit (by eye) to the envelope of the radial functions. The thick black short vertical dashed lines indicate the transition points as predicted by the empirically derived relation for the non-locality parameter $\beta_0={\rm min}(180^\circ,180^\circ \times 22/\ell_{\rm max})$.  We show moving averages over oscillations in \fig{fig:fbeta_avg} and  \fig{fig:dfbeta_avg}.  They depict the radial functions $\langle{_{\mm}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ and $\langle{_{\md}f}(\beta,\ell_{\rm min},\ell_{\rm max})\rangle$ respectively where $\langle \cdots \rangle$ denotes a moving average over a step function centered at $\beta$ with a width $\beta_0$. These smoothed functions are seen to be well fit by a power law $\propto \beta^{-2}$  and depict the average radial response.}
\label{fig:rad_ker_decay}
\end{figure}
%
